The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Removed chart
Bibtex edits

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "October 24, 2014"
output: html_document
bibliography: Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/')

@@

<p align="center">
[<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
</p>
<p align="center">
Source: OECD Local Entrepreneurship Reviews [@OECD2009]
</p>

>>>>

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "October 24, 2014"
output: html_document
bibliography: 
  - Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/')

@@
